Redundant calibration as a complex optimization problem

### 2017-12-18 paper.tex
final edit from Gianni

\section*{Acknowledgements}
This work is based upon research supported by the South
African Research Chairs Initiative of the Department of Sci-
ence and Technology and National Research Foundation.

G.B. acknowledges support from the Royal Society and the Newton Fund under grant NA150184. This work is based on the research supported in part by the National Research Foundation of South Africa (grant No. 103424). This research is supported by the South African Research Chairs Initiative of the Department of Science and Technology and National Research Foundation,

@@

Furthermore,
\begin{align}
\label{eq:identities}
\frac{1}{3}\bJ\breve{\bz} &= \breve{\bv}, & \bJ^H\breve{\bv} &= (\bI\odot\bH)\breve{\bz} 
\end{align}
The above identities can be trivially established by mechanically showing that the left hand side of each expression in equation~\ref{eq:identities} is equal to its right hand side.
In equation~\ref{eq:identities}.

>>>>

\section*{Acknowledgements}
This work is based upon research supported by the South African Research Chairs Initiative of the Department of Science and Technology and National Research Foundation. GB acknowledges support from the Royal Society and the Newton Fund under grant NA150184. This work is based on the research supported in part by the National Research Foundation of South Africa (grant No. 103424).

@@

Furthermore,
\begin{align}
\label{eq:identities}
\frac{1}{3}\bJ\breve{\bz} &= \breve{\bv}, & \bJ^H\breve{\bv} &= (\bI\odot\bH)\breve{\bz} 
\end{align}
The above identities can be trivially established by mechanically showing that the left hand side of each expression in equation~\ref{eq:identities} is equal to its right hand side.
